The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-02-13 Manuscript/manuscript.tex
Update manuscript.tex

\jy{add some references from google scholar search ``home team
  advantage nba''; we have only 10 references now.}

@@

Some studies focus less on shooting and more on other metrics.
For example, \citet{Greer} focused on the influence of spectator booing on
home-court advantage in basketball. The three methods of performance used
in this study were scoring, violations, and turnovers. This study was conducted
using the men's basketball programs at two large universities. The study finds that
social support, like booing, is an important contributor to home-court advantage.
Greer explains, whether the influence is greater on visiting team performance or
referee calls is less clear. However, the data does seem to lean slightly in
favor of affecting visiting team performance. Another study focused on scoring
was conducted by \citet{Jones}. \citet{Jones} analyzed scoring patterns across each of the 
4 quarters to analyze the effects of home-court advantage over the course of a game.
He found that typically 2/3 of the benefits of home-court advantage are received in 
the first quarter with the remaining 1/3 slowly accumulating over the 
final 3 quarters. This implies home-court advantage is most effective when teams 
use it to build a lead they then just have to maintain for the remainder of the game.
If they are losing after the first quarter, there is a sharp drop in win probability.

@@

There are a few examples of natural experiments in basketball. \citet{Harville} studied the
effect of home-court advantage using the 1991-1992 college basketball season.
Unlike the NBA, it is not uncommon to have a few games played at neutral sites
during the college basketball season. This allowed them to construct two samples,
one of home teams and one of neutral teams. They formulated their study in a
regression predicting the expected difference in score for home teams.
They set up their study to find if the home teams won games by more points when
they had home-court advantage vs.~when playing on a neutral court. This study
concluded with evidence supporting home-court advantage. Also, \citet{Boudreaux}
is able to construct a natural experiment using the Los Angeles Lakers and Los
Angeles Clippers. Since these two teams share a home stadium, many factors like 
travel and familiarity are nullified. However, the designated home team has larger
crowd support due to attendance from their season ticket holders. When they
single out the effect of having a sympathetic crowd, \citet{Boudreaux} estimate crowd 
effects increase the chance of winning 21--22.8 percentage points.

>>>>

@@

Some studies focus less on shooting and more on other metrics.
For example, \citet{Greer} focused on the influence of spectator booing on
home-court advantage in basketball. The three methods of performance used
in this study were scoring, violations, and turnovers. This study was conducted
using the men's basketball programs at two large universities. The study finds that
social support, like booing, is an important contributor to home-court advantage.
Greer explains, whether the influence is greater on visiting team performance or
referee calls is less clear. However, the data does seem to lean slightly in
favor of affecting visiting team performance. Another study focused
on scoring was conducted by \citet{Jones}, he analyzes scoring patterns across
each of the 4 quarters to analyze the effects of home-court advantage over
the course of a game. He found that typically 2/3 of the benefits of 
home-court advantage are received in the first quarter with the 
remaining 1/3 slowly accumulating over the final 3 quarters. This implies
home-court advantage is most effective when teams use it to build a 
lead early and maintain it for the remainder of the game. If they are 
losing after the first quarter, there is a sharp drop in win probability.

@@

There are a few examples of natural experiments in basketball. \citet{Harville} studied the
effect of home-court advantage using the 1991-1992 college basketball season.
Unlike the NBA, it is not uncommon to have a few games played at neutral sites
during the college basketball season. This allowed them to construct two samples,
one of home teams and one of neutral teams. They formulated their study in a
regression predicting the expected difference in score for home teams.
They set up their study to find if the home teams won games by more points when
they had home-court advantage vs.~when playing on a neutral court. This study
concluded with evidence supporting home-court advantage. Also, \citet{Boudreaux} 
is able to construct a natural experiment using the Los Angeles Lakers and 
Los Angeles Clippers. Since these two teams share a home stadium, many factors like travel 
and familiarity are nullified. However, the designated home team has larger crowd
support due to attendance from their season ticket holders. By comparing
Lakers--Clippers matchups, they single out the effect of having a sympathetic
crowd and \citet{Boudreaux} estimate crowd effects increase the chance
of winning 21--22.8 percentage points.
